Output Summary

### 2025-05-05 03-post-process/output-plots-children/02-mcmc-diags.Rmd
Minor Rmd updates after testing smallest MCMC settings

# function to plot a histogram of rhat values
rhat_hist = function(rhat) {
  # par(mgp = c(2,0.35, 0), tcl = -0.15, xaxs = "i", yaxs = "i", mar = c(3,3,1,1))
  mypar(xaxs = "i", yaxs = "i", mfrow = c(1,1))
  breaks = seq(min(rhat), max(rhat), length = 20)
  max_count = max(hist(rhat, breaks = breaks, plot = FALSE)$count)
  hist(rhat, breaks = breaks, col = "grey50", border = "white", ylim = c(0, max_count) * 1.025, main = "")
  axis_labels(xlab = "Rhat", ylab = "Frequency")
  usr = par("usr")
  segments(usr[1], usr[3], usr[2], usr[3], xpd = TRUE, col = par("col.axis"))
  segments(usr[1], usr[3], usr[1], usr[4], xpd = TRUE, col = par("col.axis"))
}
```

>>>>

# function to plot a histogram of rhat values
rhat_hist = function(rhat) {
  # par(mgp = c(2,0.35, 0), tcl = -0.15, xaxs = "i", yaxs = "i", mar = c(3,3,1,1))
  mypar(xaxs = "i", yaxs = "i", mfrow = c(1,1))
  breaks = seq(min(rhat[rhat != Inf]), max(rhat[rhat != Inf]), length = 20)
  max_count = max(hist(rhat, breaks = breaks, plot = FALSE)$count)
  hist(rhat, breaks = breaks, col = "grey50", border = "white", ylim = c(0, max_count) * 1.025, main = "")
  axis_labels(xlab = "Rhat", ylab = "Frequency")
  usr = par("usr")
  segments(usr[1], usr[3], usr[2], usr[3], xpd = TRUE, col = par("col.axis"))
  segments(usr[1], usr[3], usr[1], usr[4], xpd = TRUE, col = par("col.axis"))
}
```
